The title

### 2023-04-13 doc/multiverse.Rmd
Automate docs
Co-authored-by: James Conigrave <12742211+conig@users.noreply.github.com>

Should prevent the cases where the images are being renamed
and not matching the files.

```{r load-targets, include=FALSE}
model_list_by_age_fixedef <- tar_read(model_list_by_age_fixedef)
tar_load(data_clean)
tar_load(purdy_pictures_by_age_fixedef)
model_tables <- tar_read(model_tables_fixedef)
pretty <- function(x) format(x, big.mark = ",")
```

@@

```{r}
n_participants <- length(unique(data_clean$participant_id))
```

@@

## Multiverse

@@

## The effects of physical activity volume on sleep

We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models
We estimated the effect of physical activity volume on sleep by age, and the results are presented in Table \@ref(tab:sleep-outcomes) and Figure \@ref(fig:sleep-by-volume-fig)

```{r sleep-outcomes}
papaja::apa_table(
  model_tables$sleep$data,
  caption = model_tables$sleep$caption,
  note = model_tables$sleep$note,
  col_spanners = model_tables$sleep$col_spanners,
  escape = FALSE,
  landscape = TRUE
)
```

```{r sleep-by-volume-fig, fig.cap = "Sleep metrics on Physical activity volume"}
knitr::include_graphics(here::here("Figures/sleep on pa_volume by Age_fixedef.jpg"), error = FALSE)
```

## The effects of physical activity intensity on sleep

We estimated how physical activity intensity affects sleep across different age groups
We present the results controlling for sex, SES, and BMI, in Table \@ref(tab:sleep-outcomes) and Figure \@ref(fig:sleep-by-intensity-fig).

```{r sleep-by-intensity-fig, fig.cap = "Sleep metrics on Physical activity intensity"}
knitr::include_graphics(here::here("Figures/sleep on pa_intensity by Age_fixedef.jpg"), error = FALSE)
```

## The effects of sleep duration on physical activity

We estimated the effect of sleep duration on physical activity by age
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-duration-fig).

```{r pa-outcomes}
papaja::apa_table(
  model_tables$physical_activity$data,
  caption = model_tables$physical_activity$caption,
  note = model_tables$physical_activity$note,
  col_spanners = model_tables$physical_activity$col_spanners,
  escape = FALSE,
  landscape = TRUE
)
```

```{r PA-by-sleep-duration-fig, fig.cap = "Physical activity by sleep duration"}
knitr::include_graphics(here::here("Figures/PA on sleep_duration_lag by Age_fixedef.jpg"), error = FALSE)
```

## The effects of sleep efficiency on physical activity

We estimated the effect of sleep efficiency on physical activity by age.
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-efficiency-fig).

```{r PA-by-sleep-efficiency-fig, fig.cap = "Physical activity by sleep efficiency"}
knitr::include_graphics(here::here("Figures/PA on sleep_efficiency_lag by Age_fixedef.jpg"), error = FALSE)
```

## The effects of sleep onset on physical activity

We estimated the effect of sleep onset on physical activity by age
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-onset-fig).

```{r PA-by-sleep-onset-fig, fig.cap = "Physical activity by sleep onset"}
knitr::include_graphics(here::here("Figures/PA on sleep_onset_lag by Age_fixedef.jpg"), error = FALSE)
```

## The effects of sleep regularity on physical activity

We estimated the effect of sleep regularity on physical activity by age.
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-regularity-fig).

```{r PA-by-sleep-regularity-fig, fig.cap = "Physical activity by sleep regularity"}
knitr::include_graphics(here::here("Figures/PA on sleep_regularity_lag by Age_fixedef.jpg"), error = FALSE)
```

@@

In the following section we present models for a range of moderators which were pre-defined in our protocol.

```{r eval = FALSE}
pattern <- readLines(fs::path("doc/results_chunk.md")) |> paste(collapse = "\n")

moderator_df <- data.frame(
  moderator = c("bmi", "ses", "sex", "weekday", "season", "region", "daylight", "wear_location", "pa_mostactivehr"),
  moderator_formal = c("BMI", "SES", "sex", "weekday", "season", "region", "daylight hours", "wear location", "most active hour"),
  image_path = c("Bmi", "Ses", "Sex", "Weekday_x", "Season", "Region", "Daylight_hours", "Acc_wear_loc", "Pa_mostactivehr")
)

lapply(seq_len(nrow(moderator_df)), function(r) {
  moderator <- moderator_df$moderator[r]
  moderator_fig <- gsub("_", "-", moderator)
  moderator_formal <- moderator_df$moderator_formal[r]
  image_path <- moderator_df$image_path[r]

  glue::glue(pattern, .open = "_::", .close = "::_")
}) |>
  paste(collapse = "\n") |>
  clipr::write_clip()
```

<!------------------------------------>
<!-- Auto-generated chunks go here: -->
<!------------------------------------>

\clearpage

@@

```{r}
tar_load(model_tables_bmi)
```

@@

We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models
We estimated the effect of physical activity volume on sleep by BMI, and the results are presented in Table \@ref(tab:sleep-outcomes-by-bmi) and Figure \@ref(fig:sleep-by-volume-fig-by-bmi)

```{r sleep-outcomes-by-bmi}
papaja::apa_table(
  model_tables_bmi$sleep$data,
  caption = model_tables_bmi$sleep$caption,
  note = model_tables_bmi$sleep$note,
  col_spanners = model_tables_bmi$sleep$col_spanners,
  escape = FALSE,
  landscape = TRUE
)
```

```{r sleep-by-volume-fig-by-bmi, fig.cap = "Sleep metrics on Physical activity volume by BMI"}
knitr::include_graphics(here::here("Figures/Sleep on pa_volume by Bmi.jpg"), error = FALSE)
```

@@

We estimated how physical activity intensity affects sleep across BMI
We present the results in Table \@ref(tab:sleep-outcomes-by-bmi) and Figure \@ref(fig:sleep-by-intensity-fig-by-bmi).

```{r sleep-by-intensity-fig-by-bmi, fig.cap = "Sleep metrics on Physical activity intensity moderated by BMI"}
knitr::include_graphics(here::here("Figures/Sleep on pa_intensity by Bmi.jpg"), error = FALSE)
```

@@

We estimated the effect of sleep duration on physical activity by BMI
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-bmi) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-bmi).

```{r pa-outcomes-by-bmi}
papaja::apa_table(
  model_tables_bmi$physical_activity$data,
  caption = model_tables_bmi$physical_activity$caption,
  note = model_tables_bmi$physical_activity$note,
  col_spanners = model_tables_bmi$physical_activity$col_spanners,
  escape = FALSE,
  landscape = TRUE
)
```

```{r PA-by-sleep-duration-fig-by-bmi, fig.cap = "Physical activity by sleep duration moderated by BMI"}
knitr::include_graphics(here::here("Figures/Pa on sleep_duration_lag by Bmi.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-efficiency-fig-by-bmi, fig.cap = "Physical activity by sleep efficiency moderated by BMI"}
knitr::include_graphics(here::here("Figures/Pa on sleep_efficiency_lag by Bmi.jpg"), error = FALSE)
```

@@

We estimated the effect of sleep onset on physical activity by BMI
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-onset-fig-by-bmi).

```{r PA-by-sleep-onset-fig-by-bmi, fig.cap = "Physical activity by sleep onset moderated by BMI"}
knitr::include_graphics(here::here("Figures/Pa on sleep_onset_lag by Bmi.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-regularity-fig-by-bmi, fig.cap = "Physical activity by sleep regularity moderated by BMI"}
knitr::include_graphics(here::here("Figures/Pa on sleep_regularity_lag by Bmi.jpg"), error = FALSE)
```
\clearpage

@@

```{r}
tar_load(model_tables_ses)
```

@@

We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models
We estimated the effect of physical activity volume on sleep by SES, and the results are presented in Table \@ref(tab:sleep-outcomes-by-ses) and Figure \@ref(fig:sleep-by-volume-fig-by-ses)

```{r sleep-outcomes-by-ses}
papaja::apa_table(
  model_tables_ses$sleep$data,
  caption = model_tables_ses$sleep$caption,
  note = model_tables_ses$sleep$note,
  col_spanners = model_tables_ses$sleep$col_spanners,
  escape = FALSE,
  landscape = TRUE
)
```

```{r sleep-by-volume-fig-by-ses, fig.cap = "Sleep metrics on Physical activity volume by SES"}
knitr::include_graphics(here::here("Figures/Sleep on pa_volume by Ses.jpg"), error = FALSE)
```

@@

We estimated how physical activity intensity affects sleep across SES
We present the results in Table \@ref(tab:sleep-outcomes-by-ses) and Figure \@ref(fig:sleep-by-intensity-fig-by-ses).

```{r sleep-by-intensity-fig-by-ses, fig.cap = "Sleep metrics on Physical activity intensity moderated by SES"}
knitr::include_graphics(here::here("Figures/Sleep on pa_intensity by Ses.jpg"), error = FALSE)
```

@@

We estimated the effect of sleep duration on physical activity by SES
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-ses) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-ses).

```{r pa-outcomes-by-ses}
papaja::apa_table(
  model_tables_ses$physical_activity$data,
  caption = model_tables_ses$physical_activity$caption,
  note = model_tables_ses$physical_activity$note,
  col_spanners = model_tables_ses$physical_activity$col_spanners,
  escape = FALSE,
  landscape = TRUE
)
```

```{r PA-by-sleep-duration-fig-by-ses, fig.cap = "Physical activity by sleep duration moderated by SES"}
knitr::include_graphics(here::here("Figures/Pa on sleep_duration_lag by Ses.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-efficiency-fig-by-ses, fig.cap = "Physical activity by sleep efficiency moderated by SES"}
knitr::include_graphics(here::here("Figures/Pa on sleep_efficiency_lag by Ses.jpg"), error = FALSE)
```

@@

We estimated the effect of sleep onset on physical activity by SES
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-onset-fig-by-ses).

```{r PA-by-sleep-onset-fig-by-ses, fig.cap = "Physical activity by sleep onset moderated by SES"}
knitr::include_graphics(here::here("Figures/Pa on sleep_onset_lag by Ses.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-regularity-fig-by-ses, fig.cap = "Physical activity by sleep regularity moderated by SES"}
knitr::include_graphics(here::here("Figures/Pa on sleep_regularity_lag by Ses.jpg"), error = FALSE)
```
\clearpage

@@

```{r}
tar_load(model_tables_sex)
```

@@

We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models
We estimated the effect of physical activity volume on sleep by sex, and the results are presented in Table \@ref(tab:sleep-outcomes-by-sex) and Figure \@ref(fig:sleep-by-volume-fig-by-sex)

```{r sleep-outcomes-by-sex}
papaja::apa_table(
  model_tables_sex$sleep$data,
  caption = model_tables_sex$sleep$caption,
  note = model_tables_sex$sleep$note,
  col_spanners = model_tables_sex$sleep$col_spanners,
  escape = FALSE,
  landscape = TRUE
)
```

```{r sleep-by-volume-fig-by-sex, fig.cap = "Sleep metrics on Physical activity volume by sex"}
knitr::include_graphics(here::here("Figures/Sleep on pa_volume by Sex.jpg"), error = FALSE)
```

@@

We estimated how physical activity intensity affects sleep across sex
We present the results in Table \@ref(tab:sleep-outcomes-by-sex) and Figure \@ref(fig:sleep-by-intensity-fig-by-sex).

```{r sleep-by-intensity-fig-by-sex, fig.cap = "Sleep metrics on Physical activity intensity moderated by sex"}
knitr::include_graphics(here::here("Figures/Sleep on pa_intensity by Sex.jpg"), error = FALSE)
```

@@

We estimated the effect of sleep duration on physical activity by sex
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-sex) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-sex).

```{r pa-outcomes-by-sex}
papaja::apa_table(
  model_tables_sex$physical_activity$data,
  caption = model_tables_sex$physical_activity$caption,
  note = model_tables_sex$physical_activity$note,
  col_spanners = model_tables_sex$physical_activity$col_spanners,
  escape = FALSE,
  landscape = TRUE
)
```

```{r PA-by-sleep-duration-fig-by-sex, fig.cap = "Physical activity by sleep duration moderated by sex"}
knitr::include_graphics(here::here("Figures/Pa on sleep_duration_lag by Sex.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-efficiency-fig-by-sex, fig.cap = "Physical activity by sleep efficiency moderated by sex"}
knitr::include_graphics(here::here("Figures/Pa on sleep_efficiency_lag by Sex.jpg"), error = FALSE)
```

@@

We estimated the effect of sleep onset on physical activity by sex
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-onset-fig-by-sex).

```{r PA-by-sleep-onset-fig-by-sex, fig.cap = "Physical activity by sleep onset moderated by sex"}
knitr::include_graphics(here::here("Figures/Pa on sleep_onset_lag by Sex.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-regularity-fig-by-sex, fig.cap = "Physical activity by sleep regularity moderated by sex"}
knitr::include_graphics(here::here("Figures/Pa on sleep_regularity_lag by Sex.jpg"), error = FALSE)
```
\clearpage

@@

```{r}
tar_load(model_tables_weekday)
```

@@

We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models
We estimated the effect of physical activity volume on sleep by weekday, and the results are presented in Table \@ref(tab:sleep-outcomes-by-weekday) and Figure \@ref(fig:sleep-by-volume-fig-by-weekday)

```{r sleep-outcomes-by-weekday}
papaja::apa_table(
  model_tables_weekday$sleep$data,
  caption = model_tables_weekday$sleep$caption,
  note = model_tables_weekday$sleep$note,
  col_spanners = model_tables_weekday$sleep$col_spanners,
  escape = FALSE,
  landscape = TRUE
)
```

```{r sleep-by-volume-fig-by-weekday, fig.cap = "Sleep metrics on Physical activity volume by weekday"}
knitr::include_graphics(here::here("Figures/Sleep on pa_volume by Weekday_x.jpg"), error = FALSE)
```

@@

We estimated how physical activity intensity affects sleep across weekday
We present the results in Table \@ref(tab:sleep-outcomes-by-weekday) and Figure \@ref(fig:sleep-by-intensity-fig-by-weekday).

```{r sleep-by-intensity-fig-by-weekday, fig.cap = "Sleep metrics on Physical activity intensity moderated by weekday"}
knitr::include_graphics(here::here("Figures/Sleep on pa_intensity by Weekday_x.jpg"), error = FALSE)
```

@@

We estimated the effect of sleep duration on physical activity by weekday
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-weekday) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-weekday).

>>>>

```{r load-targets, include=FALSE}
tar_load(multiverse_file)
pretty <- function(x) format(x, big.mark = ",")
```

@@

@@

## Fixed Effect Model

```{r}
tar_load(model_tables_by_age_fixedef)
tar_load(purdy_pictures_by_age_fixedef)
```

@@

### The effects of physical activity volume on sleep

We estimated the effects of physical activity on sleep (RQ1) using fixed-effects models.
We estimated the effect of physical activity volume on sleep by age, and the results are presented in Table \@ref(tab:sleep-outcomes-fixedef) and Figure \@ref(fig:sleep-by-volume-fig-fixedef).

```{r sleep-outcomes-fixedef}
papaja::apa_table(
  model_tables_by_age_fixedef$sleep$data,
  caption = model_tables_by_age_fixedef$sleep$caption,
  note = model_tables_by_age_fixedef$sleep$note,
  col_spanners = model_tables_by_age_fixedef$sleep$col_spanners,
  escape = FALSE,
  landscape = TRUE
)
```

```{r sleep-by-volume-fig-fixedef, fig.cap = "Sleep metrics on Physical activity volume"}
knitr::include_graphics(here::here(purdy_pictures_by_age_fixedef$predictor_pa_volume), error = FALSE)
```

### The effects of physical activity intensity on sleep

We estimated how physical activity intensity affects sleep across different age groups.
We present the results controlling for sex, SES, and BMI, in Table \@ref(tab:sleep-outcomes-fixedef) and Figure \@ref(fig:sleep-by-intensity-fig-fixedef).

```{r sleep-by-intensity-fig-fixedef, fig.cap = "Sleep metrics on Physical activity intensity"}
knitr::include_graphics(here::here(purdy_pictures_by_age_fixedef$predictor_pa_intensity), error = FALSE)
```

We estimated the effect of sleep duration on physical activity by age.
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-fixedef) and Figure \@ref(fig:PA-by-sleep-duration-fig-fixedef).

```{r pa-outcomes-fixedef}
papaja::apa_table(
  model_tables_by_age_fixedef$physical_activity$data,
  caption = model_tables_by_age_fixedef$physical_activity$caption,
  note = model_tables_by_age_fixedef$physical_activity$note,
  col_spanners = model_tables_by_age_fixedef$physical_activity$col_spanners,
  escape = FALSE,
  landscape = TRUE
)
```

```{r PA-by-sleep-duration-fig-fixedef, fig.cap = "Physical activity by sleep duration"}
knitr::include_graphics(here::here(purdy_pictures_by_age_fixedef$predictor_sleep_duration_lag), error = FALSE)
```

We estimated the effect of sleep efficiency on physical activity by age.
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-fixedef) and Figure \@ref(fig:PA-by-sleep-efficiency-fig-fixedef).

```{r PA-by-sleep-efficiency-fig-fixedef, fig.cap = "Physical activity by sleep efficiency"}
knitr::include_graphics(here::here(purdy_pictures_by_age_fixedef$predictor_sleep_efficiency_lag), error = FALSE)
```

We estimated the effect of sleep onset on physical activity by age.
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-fixedef) and Figure \@ref(fig:PA-by-sleep-onset-fig-fixedef).

```{r PA-by-sleep-onset-fig-fixedef, fig.cap = "Physical activity by sleep onset"}
knitr::include_graphics(here::here(purdy_pictures_by_age_fixedef$predictor_sleep_onset_lag), error = FALSE)
```

We estimated the effect of sleep regularity on physical activity by age.
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-fixedef) and Figure \@ref(fig:PA-by-sleep-regularity-fig-fixedef).

```{r PA-by-sleep-regularity-fig-fixedef, fig.cap = "Physical activity by sleep regularity"}
knitr::include_graphics(here::here(purdy_pictures_by_age_fixedef$predictor_sleep_regularity_lag), error = FALSE)
```

## Without Log Transforming PA Volume

```{r}
tar_load(model_tables_by_age_nolog)
tar_load(purdy_pictures_by_age_nolog)
```

Based on preliminary modelling on a subset of the data, we chose to log transform the physical activity volume variable.
Below, we present the results had we not made this decision.
These results are all moderated by age, as this was our primary analysis.

### The effects of physical activity volume on sleep

We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models.
We estimated the effect of physical activity volume on sleep by age, and the results are presented in Table \@ref(tab:sleep-outcomes-nolog) and Figure \@ref(fig:sleep-by-volume-fig-nolog).

```{r sleep-outcomes-nolog}
papaja::apa_table(
  model_tables_by_age_nolog$sleep$data,
  caption = model_tables_by_age_nolog$sleep$caption,
  note = model_tables_by_age_nolog$sleep$note,
  col_spanners = model_tables_by_age_nolog$sleep$col_spanners,
  escape = FALSE,
  landscape = TRUE
)
```

```{r sleep-by-volume-fig-nolog, fig.cap = "Sleep metrics on Physical activity volume"}
knitr::include_graphics(here::here(purdy_pictures_by_age_nolog$predictor_pa_volume), error = FALSE)
```

We estimated the effect of sleep duration on physical activity by age.
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-nolog) and Figure \@ref(fig:PA-by-sleep-duration-fig-nolog).

```{r pa-outcomes-nolog}
papaja::apa_table(
  model_tables_by_age_nolog$physical_activity$data,
  caption = model_tables_by_age_nolog$physical_activity$caption,
  note = model_tables_by_age_nolog$physical_activity$note,
  col_spanners = model_tables_by_age_nolog$physical_activity$col_spanners,
  escape = FALSE,
  landscape = TRUE
)
```

```{r PA-by-sleep-duration-fig-nolog, fig.cap = "Physical activity by sleep duration"}
knitr::include_graphics(here::here(purdy_pictures_by_age_nolog$predictor_sleep_duration_lag), error = FALSE)
```

We estimated the effect of sleep efficiency on physical activity by age.
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-nolog) and Figure \@ref(fig:PA-by-sleep-efficiency-fig-nolog).

```{r PA-by-sleep-efficiency-fig-nolog, fig.cap = "Physical activity by sleep efficiency"}
knitr::include_graphics(here::here(purdy_pictures_by_age_nolog$predictor_sleep_efficiency_lag), error = FALSE)
```

We estimated the effect of sleep onset on physical activity by age.
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-nolog) and Figure \@ref(fig:PA-by-sleep-onset-fig-nolog).

```{r PA-by-sleep-onset-fig-nolog, fig.cap = "Physical activity by sleep onset"}
knitr::include_graphics(here::here(purdy_pictures_by_age_nolog$predictor_sleep_onset_lag), error = FALSE)
```

We estimated the effect of sleep regularity on physical activity by age.
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-nolog) and Figure \@ref(fig:PA-by-sleep-regularity-fig-nolog).

```{r PA-by-sleep-regularity-fig-nolog, fig.cap = "Physical activity by sleep regularity"}
knitr::include_graphics(here::here(purdy_pictures_by_age_nolog$predictor_sleep_regularity_lag), error = FALSE)
```

@@

In the following section we present models for a range of moderators which were pre-defined in our protocol.
\clearpage

@@

```{r}
tar_load(model_tables_by_bmi)
tar_load(purdy_pictures_by_bmi)
```

@@

We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models.
We estimated the effect of physical activity volume on sleep by BMI, and the results are presented in Table \@ref(tab:sleep-outcomes-by-bmi) and Figure \@ref(fig:sleep-by-volume-fig-by-bmi)

```{r sleep-outcomes-by-bmi}
papaja::apa_table(
  model_tables_by_bmi$sleep$data,
  caption = model_tables_by_bmi$sleep$caption,
  note = model_tables_by_bmi$sleep$note,
  col_spanners = model_tables_by_bmi$sleep$col_spanners,
  escape = FALSE,
  landscape = TRUE
)
```

```{r sleep-by-volume-fig-by-bmi, fig.cap = "Sleep metrics on Physical activity volume by BMI"}
knitr::include_graphics(here::here(purdy_pictures_by_bmi$predictor_pa_volume), error = FALSE)
```

@@

We estimated how physical activity intensity affects sleep across BMI.
We present the results in Table \@ref(tab:sleep-outcomes-by-bmi) and Figure \@ref(fig:sleep-by-intensity-fig-by-bmi).

```{r sleep-by-intensity-fig-by-bmi, fig.cap = "Sleep metrics on Physical activity intensity moderated by BMI"}
knitr::include_graphics(here::here(purdy_pictures_by_bmi$predictor_pa_intensity), error = FALSE)
```

@@

We estimated the effect of sleep duration on physical activity by BMI.
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-bmi) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-bmi).

```{r pa-outcomes-by-bmi}
papaja::apa_table(
  model_tables_by_bmi$physical_activity$data,
  caption = model_tables_by_bmi$physical_activity$caption,
  note = model_tables_by_bmi$physical_activity$note,
  col_spanners = model_tables_by_bmi$physical_activity$col_spanners,
  escape = FALSE,
  landscape = TRUE
)
```

```{r PA-by-sleep-duration-fig-by-bmi, fig.cap = "Physical activity by sleep duration moderated by BMI"}
knitr::include_graphics(here::here(purdy_pictures_by_bmi$predictor_sleep_duration_lag), error = FALSE)
```

@@

```{r PA-by-sleep-efficiency-fig-by-bmi, fig.cap = "Physical activity by sleep efficiency moderated by BMI"}
knitr::include_graphics(here::here(purdy_pictures_by_bmi$predictor_sleep_efficiency_lag), error = FALSE)
```

@@

We estimated the effect of sleep onset on physical activity by BMI.
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-bmi) and Figure \@ref(fig:PA-by-sleep-onset-fig-by-bmi).

```{r PA-by-sleep-onset-fig-by-bmi, fig.cap = "Physical activity by sleep onset moderated by BMI"}
knitr::include_graphics(here::here(purdy_pictures_by_bmi$predictor_sleep_onset_lag), error = FALSE)
```

@@

```{r PA-by-sleep-regularity-fig-by-bmi, fig.cap = "Physical activity by sleep regularity moderated by BMI"}
knitr::include_graphics(here::here(purdy_pictures_by_bmi$predictor_sleep_regularity_lag), error = FALSE)
```
\clearpage

@@

```{r}
tar_load(model_tables_by_ses)
tar_load(purdy_pictures_by_ses)
```

@@

We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models.
We estimated the effect of physical activity volume on sleep by SES, and the results are presented in Table \@ref(tab:sleep-outcomes-by-ses) and Figure \@ref(fig:sleep-by-volume-fig-by-ses)

```{r sleep-outcomes-by-ses}
papaja::apa_table(
  model_tables_by_ses$sleep$data,
  caption = model_tables_by_ses$sleep$caption,
  note = model_tables_by_ses$sleep$note,
  col_spanners = model_tables_by_ses$sleep$col_spanners,
  escape = FALSE,
  landscape = TRUE
)
```

```{r sleep-by-volume-fig-by-ses, fig.cap = "Sleep metrics on Physical activity volume by SES"}
knitr::include_graphics(here::here(purdy_pictures_by_ses$predictor_pa_volume), error = FALSE)
```

@@

We estimated how physical activity intensity affects sleep across SES.
We present the results in Table \@ref(tab:sleep-outcomes-by-ses) and Figure \@ref(fig:sleep-by-intensity-fig-by-ses).

```{r sleep-by-intensity-fig-by-ses, fig.cap = "Sleep metrics on Physical activity intensity moderated by SES"}
knitr::include_graphics(here::here(purdy_pictures_by_ses$predictor_pa_intensity), error = FALSE)
```

@@

We estimated the effect of sleep duration on physical activity by SES.
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-ses) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-ses).

```{r pa-outcomes-by-ses}
papaja::apa_table(
  model_tables_by_ses$physical_activity$data,
  caption = model_tables_by_ses$physical_activity$caption,
  note = model_tables_by_ses$physical_activity$note,
  col_spanners = model_tables_by_ses$physical_activity$col_spanners,
  escape = FALSE,
  landscape = TRUE
)
```

```{r PA-by-sleep-duration-fig-by-ses, fig.cap = "Physical activity by sleep duration moderated by SES"}
knitr::include_graphics(here::here(purdy_pictures_by_ses$predictor_sleep_duration_lag), error = FALSE)
```

@@

```{r PA-by-sleep-efficiency-fig-by-ses, fig.cap = "Physical activity by sleep efficiency moderated by SES"}
knitr::include_graphics(here::here(purdy_pictures_by_ses$predictor_sleep_efficiency_lag), error = FALSE)
```

@@

We estimated the effect of sleep onset on physical activity by SES.
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-ses) and Figure \@ref(fig:PA-by-sleep-onset-fig-by-ses).

```{r PA-by-sleep-onset-fig-by-ses, fig.cap = "Physical activity by sleep onset moderated by SES"}
knitr::include_graphics(here::here(purdy_pictures_by_ses$predictor_sleep_onset_lag), error = FALSE)
```

@@

```{r PA-by-sleep-regularity-fig-by-ses, fig.cap = "Physical activity by sleep regularity moderated by SES"}
knitr::include_graphics(here::here(purdy_pictures_by_ses$predictor_sleep_regularity_lag), error = FALSE)
```
\clearpage

@@

```{r}
tar_load(model_tables_by_sex)
tar_load(purdy_pictures_by_sex)
```

@@

We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models.
We estimated the effect of physical activity volume on sleep by sex, and the results are presented in Table \@ref(tab:sleep-outcomes-by-sex) and Figure \@ref(fig:sleep-by-volume-fig-by-sex)

```{r sleep-outcomes-by-sex}
papaja::apa_table(
  model_tables_by_sex$sleep$data,
  caption = model_tables_by_sex$sleep$caption,
  note = model_tables_by_sex$sleep$note,
  col_spanners = model_tables_by_sex$sleep$col_spanners,
  escape = FALSE,
  landscape = TRUE
)
```

```{r sleep-by-volume-fig-by-sex, fig.cap = "Sleep metrics on Physical activity volume by sex"}
knitr::include_graphics(here::here(purdy_pictures_by_sex$predictor_pa_volume), error = FALSE)
```

@@

We estimated how physical activity intensity affects sleep across sex.
We present the results in Table \@ref(tab:sleep-outcomes-by-sex) and Figure \@ref(fig:sleep-by-intensity-fig-by-sex).

```{r sleep-by-intensity-fig-by-sex, fig.cap = "Sleep metrics on Physical activity intensity moderated by sex"}
knitr::include_graphics(here::here(purdy_pictures_by_sex$predictor_pa_intensity), error = FALSE)
```

@@

We estimated the effect of sleep duration on physical activity by sex.
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-sex) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-sex).

```{r pa-outcomes-by-sex}
papaja::apa_table(
  model_tables_by_sex$physical_activity$data,
  caption = model_tables_by_sex$physical_activity$caption,
  note = model_tables_by_sex$physical_activity$note,
  col_spanners = model_tables_by_sex$physical_activity$col_spanners,
  escape = FALSE,
  landscape = TRUE
)
```

```{r PA-by-sleep-duration-fig-by-sex, fig.cap = "Physical activity by sleep duration moderated by sex"}
knitr::include_graphics(here::here(purdy_pictures_by_sex$predictor_sleep_duration_lag), error = FALSE)
```

@@

```{r PA-by-sleep-efficiency-fig-by-sex, fig.cap = "Physical activity by sleep efficiency moderated by sex"}
knitr::include_graphics(here::here(purdy_pictures_by_sex$predictor_sleep_efficiency_lag), error = FALSE)
```

@@

We estimated the effect of sleep onset on physical activity by sex.
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-sex) and Figure \@ref(fig:PA-by-sleep-onset-fig-by-sex).

```{r PA-by-sleep-onset-fig-by-sex, fig.cap = "Physical activity by sleep onset moderated by sex"}
knitr::include_graphics(here::here(purdy_pictures_by_sex$predictor_sleep_onset_lag), error = FALSE)
```

@@

```{r PA-by-sleep-regularity-fig-by-sex, fig.cap = "Physical activity by sleep regularity moderated by sex"}
knitr::include_graphics(here::here(purdy_pictures_by_sex$predictor_sleep_regularity_lag), error = FALSE)
```
\clearpage

@@

```{r}
tar_load(model_tables_by_weekday)
tar_load(purdy_pictures_by_weekday)
```

@@

We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models.
We estimated the effect of physical activity volume on sleep by weekday, and the results are presented in Table \@ref(tab:sleep-outcomes-by-weekday) and Figure \@ref(fig:sleep-by-volume-fig-by-weekday)

```{r sleep-outcomes-by-weekday}
papaja::apa_table(
  model_tables_by_weekday$sleep$data,
  caption = model_tables_by_weekday$sleep$caption,
  note = model_tables_by_weekday$sleep$note,
  col_spanners = model_tables_by_weekday$sleep$col_spanners,
  escape = FALSE,
  landscape = TRUE
)
```

```{r sleep-by-volume-fig-by-weekday, fig.cap = "Sleep metrics on Physical activity volume by weekday"}
knitr::include_graphics(here::here(purdy_pictures_by_weekday$predictor_pa_volume), error = FALSE)
```

@@

We estimated how physical activity intensity affects sleep across weekday.
We present the results in Table \@ref(tab:sleep-outcomes-by-weekday) and Figure \@ref(fig:sleep-by-intensity-fig-by-weekday).

```{r sleep-by-intensity-fig-by-weekday, fig.cap = "Sleep metrics on Physical activity intensity moderated by weekday"}
knitr::include_graphics(here::here(purdy_pictures_by_weekday$predictor_pa_intensity), error = FALSE)
```

@@

We estimated the effect of sleep duration on physical activity by weekday.
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-weekday) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-weekday).

```{r pa-outcomes-by-weekday}
papaja::apa_table(
  model_tables_by_weekday$physical_activity$data,
  caption = model_tables_by_weekday$physical_activity$caption,
  note = model_tables_by_weekday$physical_activity$note,
  col_spanners = model_tables_by_weekday$physical_activity$col_spanners,
  escape = FALSE,
  landscape = TRUE
)
```
